### 2016-04-01 project report/LNCS-template/paper.tex
report

\documentclass[runningheads,a4paper]{llncs}

\usepackage[american]{babel}

%better font, similar to the default springer font
%cfr-lm is preferred over lmodern. Reasoning at http://tex.stackexchange.com/a/247543/9075
\usepackage[%
rm={oldstyle=false,proportional=true},%
sf={oldstyle=false,proportional=true},%
tt={oldstyle=false,proportional=true,variable=true},%
qt=false%
]{cfr-lm}
%
%if more space is needed, exchange cfr-lm by mathptmx
%\usepackage{mathptmx}

\usepackage{graphicx}

%extended enumerate, such as \begin{compactenum}
\usepackage{paralist}

%put figures inside a text
%\usepackage{picins}
%use
%\piccaptioninside
%\piccaption{...}
%\parpic[r]{\includegraphics ...}
%Text...

%Sorts the citations in the brackets
%\usepackage{cite}

%for easy quotations: \enquote{text}
\usepackage{csquotes}

\usepackage[T1]{fontenc}

%enable margin kerning
\usepackage{microtype}

%for demonstration purposes only
\usepackage[math]{blindtext}

%tweak \url{...}
\usepackage{url}
%nicer // - solution by http://tex.stackexchange.com/a/98470/9075
\makeatletter
\def\Url@twoslashes{\mathchar`\/\@ifnextchar/{\kern-.2em}{}}
\g@addto@macro\UrlSpecials{\do\/{\Url@twoslashes}}
\makeatother
\urlstyle{same}
%improve wrapping of URLs - hint by http://tex.stackexchange.com/a/10419/9075
\makeatletter
\g@addto@macro{\UrlBreaks}{\UrlOrds}
\makeatother

%diagonal lines in a table - http://tex.stackexchange.com/questions/17745/diagonal-lines-in-table-cell
%slashbox is not available in texlive (due to licensing) and also gives bad results. This, we use diagbox
%\usepackage{diagbox}

%required for pdfcomment later
\usepackage{xcolor}

% new packages BEFORE hyperref
% See also http://tex.stackexchange.com/questions/1863/which-packages-should-be-loaded-after-hyperref-instead-of-before

%enable hyperref without colors and without bookmarks
\usepackage[
%pdfauthor={},
%pdfsubject={},
%pdftitle={},
%pdfkeywords={},
bookmarks=false,
breaklinks=true,
colorlinks=true,
linkcolor=black,
citecolor=black,
urlcolor=black,
%pdfstartpage=19,
pdfpagelayout=SinglePage,
pdfstartview=Fit
]{hyperref}
%enables correct jumping to figures when referencing
\usepackage[all]{hypcap}

%enable nice comments
\usepackage{pdfcomment}
\newcommand{\commentontext}[2]{\colorbox{yellow!60}{#1}\pdfcomment[color={0.234 0.867 0.211},hoffset=-6pt,voffset=10pt,opacity=0.5]{#2}}
\newcommand{\commentatside}[1]{\pdfcomment[color={0.045 0.278 0.643},icon=Note]{#1}}

%compatibality with TODO package
\newcommand{\todo}[1]{\commentatside{#1}}

%enable \cref{...} and \Cref{...} instead of \ref: Type of reference included in the link
\usepackage[capitalise,nameinlink]{cleveref}
%Nice formats for \cref
\crefname{section}{Sect.}{Sect.}
\Crefname{section}{Section}{Sections}
\crefname{figure}{Fig.}{Fig.}
\Crefname{figure}{Figure}{Figures}

\usepackage{xspace}
%\newcommand{\eg}{e.\,g.\xspace}
%\newcommand{\ie}{i.\,e.\xspace}
\newcommand{\eg}{e.\,g.,\ }
\newcommand{\ie}{i.\,e.,\ }

%introduce \powerset - hint by http://matheplanet.com/matheplanet/nuke/html/viewtopic.php?topic=136492&post_id=997377
\DeclareFontFamily{U}{MnSymbolC}{}
\DeclareSymbolFont{MnSyC}{U}{MnSymbolC}{m}{n}
\DeclareFontShape{U}{MnSymbolC}{m}{n}{
    <-6>  MnSymbolC5
   <6-7>  MnSymbolC6
   <7-8>  MnSymbolC7
   <8-9>  MnSymbolC8
   <9-10> MnSymbolC9
  <10-12> MnSymbolC10
  <12->   MnSymbolC12%
}{}
\DeclareMathSymbol{\powerset}{\mathord}{MnSyC}{180}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}

%Works on MiKTeX only
%hint by http://goemonx.blogspot.de/2012/01/pdflatex-ligaturen-und-copynpaste.html
%also http://tex.stackexchange.com/questions/4397/make-ligatures-in-linux-libertine-copyable-and-searchable
%This allows a copy'n'paste of the text from the paper
\input glyphtounicode.tex
\pdfgentounicode=1

\title{ECE 657A Project Report}
%If Title is too long, use \titlerunning
%\titlerunning{Short Title}

%Single insitute
\author{Laura McCrackin (20262085),Yuzhou Wang (20609396) \and Huang Tianhui (20587328)}
%If there are too many authors, use \authorrunning
%\authorrunning{First Author et al.}
\institute{University of Waterloo}

%Multiple insitutes
%Currently disabled
%
\iffalse
%Multiple institutes are typeset as follows:
%\author{Firstname Lastname\inst{1} \and Firstname Lastname\inst{2} }
%If there are too many authors, use \authorrunning
%\authorrunning{First Author et al.}

\institute{
University of Waterloo\\
\email{...}\and
University of Waterloo\\
\email{...}
}
\fi

\maketitle
%%%%%%%%%%%%%   abstract need to be added!!!! %%%%%%%%%
\begin{abstract}
Traditionally, there are several methods to sovle the question answering problem. In our project, we are aiming to solve this problem by nueral network in attentive model.
\keywords{Deep Learning, Nueral Network, NLP}
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\blindtext\todo{Refine me}

%Winery~\cite{Winery} is graphical \commentontext{modeling}{modeling with one \enquote{l}, because of AE} tool.

Natural Language Processing (NLP), as one of the artificial intelligence topic, is becoming more and more popular recently. It can also be divided into several parts like text to speech, speech recognition, information retrieval, etc. Our project focuses on getting the information from a passage of text. Our project is aimed to training machine to Read and Comprehend. When an article is given, the machine could automatically answer the questions. This project is one of the topic in Nature language processing, enabling computers to derive meaning from human or natural language input.  
Dataset: In our project, we will be working with question answering using the Machine Comprehension Test (MCTest) dataset created by Microsoft [1]. For the story generate, they ensured that the data is the same quality as another set and also limited the text to children’s stories, so that it could be easily understand. Limited vocabulary: The lowercase words in the story, questions, and answers were stemmed from list of approximately 8000 words that a 7 year old is likely to know. Multiple-sentence questions: At least two of the questions need multiple sentences to answer. As each story is fictional, the answers can only be found in the story itself, which requires high-level machine comprehension without any world knowledge.

\section{Review of literature}
\subsubsection*{ Traditional baseline methods}
Majority baseline (maximum frequency) picks the entity most frequently observed in the context document.
Exclusive majority (exclusive frequency) chooses the entity most frequently observed in the context but not observed in the query. The idea behind this exclusion is that the placeholder is unlikely to be mentioned twice in a single Cloze form query[2]. 
Word Distance Benchmark: The main idea is that choose the shortest distance among all of the answers to the question’s key words.

\subsubsection*{ Traditional Frame-Semantic Parsing}
Frame-semantic parsing attempts to identify predicates and their arguments, allowing models access to information about “who did what to whom”. And we could see some of the language strategy patterns as below.

%%%%%%%%need to add figure

But this method has some limitations for can not possess the capability to generalize through a language model beyond exploiting one during the parsing phase[2]. And what is more, teaching machines to read natural language documents remains an elusive challenge. Machine reading systems can be tested on their ability to answer questions posed on the contents of documents that they have seen, but until now large scale training and test datasets have been missing for this type of evaluation. In other words, those are limited on training dataset.

\subsubsection*{ Comprehension with Syntax, Frames, and Semantics}
Semantic: frame semantic parsing (Das et al., 2014) is aimed to extract frame-specific predicate-argument structures from sentences. [3]
Syntax: given each candidate answer, we attempt to transform the question to a statement using the  extraction rules[4].
But according to the error analysis suggests that deeper linguistic analysis and inferential reasoning can yield further improvements on this task.

\subsubsection*{ Comprehension with Discourse Relations[5]}
The model jointly identifies relevant sentences, establishes relations between them and predicts an answer. The key idea is to implant discourse analysis into a joint model for comprehension. And the drawback of this model is that the accuracy varies significantly according to the question type. Which means not really stable.

\subsubsection*{  Comprehension for Learning Answer-Entailing Structures[6]}
We posit that there is a hidden (latent) structure that explains the relation between the question, correct answer, and text. For this given structure, the correctness of the answer is evident. Since the structure is latent, it must be inferred. Firstly, we should presents a unified max-margin framework that learns to find these hidden structures (given a corpus of question-answer pairs), and then uses what it learns to answer machine comprehension questions on novel texts. But the drawback of this method is that since inference is cheaply modelled via alignment structure, we lack the ability to deeply reason about facts or numbers.

\section{Research for Neural Network}

\subsubsection*{Deep LSTM Reader Model}
The Deep LSTM Reader embed long sequences into a vector representation which contains enough information to generate a full translation in another language. The result is that this model processes each document query pair as a single long sequence. Given the embedded document and query the network predicts which token in the document answers the query. So this one is the old version of neural networking.

\subsubsection*{Impatient Reader Model}
The Impatient Reader focuses on the passages of a context document that are most likely to inform the answer to the query. We can go further by equipping the model with the ability to reread from the document as each query token is read. The result is an attention mechanism that allows the model to recurrently accumulate information from the document as it sees each query token, ultimately outputting a final joint document query representation for the answer prediction.

\subsubsection*{Attentive Reader Model}
The Attentive Reader can be viewed as a generalization of the application of Memory Networks to question answering. That model employs an attention mechanism at the sentence level where each sentence is represented by a bag of embeddings. This model could fix the bottleneck for the width of different words. This attention model first encodes the document and the query using separate bidirectional single layer LSTMs. This task has been tricky because of the number of parameters that must be fine-tuned.
Although this method cannot be backwards checking as impatient reader but according to some article, these two methods have the similar results, so our group used this model.

\section{Description of the project task and the used methods}
For data preprocessing, we use python NLTK library.
For deep learning part, we use blocks and fuels, Theano framework for deep learning part.

\section{Implementation details and experimental setup}
For preprocessing part, we firstly setup the NLTK working environment with python and later import some libraries like stem, tokenize, corpus, etc. We deal with deleting punctuation like “,” “.”,etc. Later we also extract questions pattern like “when”, “how”, etc. we change numbers into English words by dictionary. We also do the following step for text preprocessing.

\begin{inparaenum}
	\item using stop words library to remove stop words
	\item using regular expression
	\item define a function and by recursion to convert a number into a verb
	\item using library to deal with stem words
	\item using lemmatizatio: Returns the input word unchanged if it cannot be found in WordNet.
	\item dealing with rawfile and answer file input. To become like…
	\item getting the entities.
	\item preprocessing both questions and answers
\end{inparaenum}

\section{Results, performance evaluation, and analysis}

\section{Discussion of results and conclusions}

Brackets work as designed:
<test>

The symbol for powerset is now correct: $\powerset$ and not a Weierstrass p ($\wp$).

\begin{inparaenum}
\item All these items...
\item ...appear in one line
\item This is enabled by the paralist package.
\end{inparaenum}

``something in quotes'' using plain tex or use \enquote{the enquote command}.

\section{Conclusion and Outlook}

\subsubsection*{Acknowledgments}
...

In the bibliography, use \texttt{\textbackslash textsuperscript} for ``st'', ``nd'', ...:
E.g., \enquote{The 2\textsuperscript{nd} conference on examples}.
When you use \href{http://www.jabref.org}{JabRef}, you can use the clean up command to achieve that.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{splncs03}
\bibliography{paper}

All links were last followed on October 5, 2014.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%% template for figure and table
\begin{figure}
	Simple Figure
	\caption{ Figure}
	\label{fig:simple}
\end{figure}

\begin{table}
	\caption{Simple Table}

	\label{tab:simple}
	Simple Table
\end{table}
%%%%%%%%%%%%%%%%%%
cref Demonstration: Cref at beginning of sentence, cref in all other cases.

\Cref{fig:simple} shows a simple fact, although \cref{fig:simple} could also show something else.

\Cref{tab:simple} shows a simple fact, although \cref{tab:simple} could also show something else.

\Cref{sec:intro} shows a simple fact, although \cref{sec:intro} could also show something else.
%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2016-04-02 project report/LNCS-template/paper.tex
report
message

@@
 %Single insitute
-\author{Laura McCrackin (20262085),Yuzhou Wang (20609396) \and Huang Tianhui (20587328)}
+\author{Laura McCrackin (20262085),Yuzhou Wang (20609396) \and Tianhui Huang (20587328)}
 %If there are too many authors, use \authorrunning
@@
 It can also be divided into several parts like text to speech, speech recognition, information retrieval, etc.
-Our project focuses on getting the information from a passage of text.
-Our project is aimed to training machine to Read and Comprehend.
+Our project focuses on getting the information from a passage of text aiming to training machine to Read and Comprehend.
 When an article is given, the machine could automatically answer the questions.
 This project is one of the topic in Nature language processing, enabling computers to derive meaning from human or natural language input.
-Dataset: In our project, we will be working with question answering using the Machine Comprehension Test (MCTest) dataset created by Microsoft [1].
-For the story generate, they ensured that the data is the same quality as another set and also limited the text to children’s stories, so that it could be easily understand.
-Limited vocabulary: The lowercase words in the story, questions, and answers were stemmed from list of approximately 8000 words that a 7 year old is likely to know.
+
+\section{Dataset}
+We used the Machine Comprehension Test (MCTest) dataset created by Microsoft [1].
+The authors of stories are all workers, residing in the United States.
+The average worker is 36 years old, more educated than the United States population in general (Paolacci et al., 2010), and the majority of workers are female.
+Workers were instructed to write a short (150-300 words) fictional story, and to write as if for a child in grade school.
+Workers were also asked to provide four reading comprehension questions pertaining to their story and, for each, four multiple-choice answers.
+Workers were requested to provide 'reasonable' incorrect answers that at least include words from the story so that their solution is not trivial.
+Finally, workers were asked to design their questions and answers such that at least two of the four questions required multiple sentences from the story to answer them.
+That is, for those questions it should not be possible to find the answer in any individual sentence.
+The MCTest corpus contains two sets of stories, named MC160 and MC500, and containing 160 and 500 stories respectively.
+MC160 was gathered first, then some improvements were made before gathering MC500.
+Adding a Grammar Test to form the MC500.
+In addition to the details described above, MC160 workers were given a target elementary grade school level (1-4) and a sample story matching that grade level5. 
+For the story generate, they ensured that the data is the same quality as another set and also limited the text to children stories, so that it could be easily understand.The  vocabulary is also limited: the lowercase words in the story, questions, and answers were stemmed from list of approximately 8000 words that a 7 year old is likely to know.
 Multiple-sentence questions: At least two of the questions need multiple sentences to answer.
@@
 \section{Review of literature}
-\subsubsection*{ Traditional baseline methods}
-Majority baseline (maximum frequency) picks the entity most frequently observed in the context document.
+Traditional baseline methods:majority baseline (maximum frequency) picks the entity most frequently observed in the context document.
 Exclusive majority (exclusive frequency) chooses the entity most frequently observed in the context but not observed in the query.
 The idea behind this exclusion is that the placeholder is unlikely to be mentioned twice in a single Cloze form query[2].
-Word Distance Benchmark: The main idea is that choose the shortest distance among all of the answers to the question’s key words.
+Word Distance Benchmark: The main idea is that choose the shortest distance among all of the answers to the question key words.
 
-\subsubsection*{ Traditional Frame-Semantic Parsing}
-Frame-semantic parsing attempts to identify predicates and their arguments, allowing models access to information about “who did what to whom”.
-And we could see some of the language strategy patterns as below.
+There are also several traditinal methods.Firstly, it is traditional Frame-Semantic Parsing.
+Frame-semantic parsing attempts to identify predicates and their arguments, allowing models access to information about 'who did what to whom'.
+And we could see some of the language strategy patterns as figure 1.
 
-%%%%%%%%need to add figure
+\begin{figure}[p]
+	\centering
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=1\linewidth]{../parsing.png}
+		\caption{ROC}
+		\label{figure 1:Frame-Semantic Parsing}
+	\end{subfigure}
+
+\end{figure}
 
@@
 
-\subsubsection*{ Comprehension with Syntax, Frames, and Semantics}
-Semantic: frame semantic parsing (Das et al., 2014) is aimed to extract frame-specific predicate-argument structures from sentences. [3]
-Syntax: given each candidate answer, we attempt to transform the question to a statement using the  extraction rules[4].
+Other people also have the idea of comprehension with Syntax, Frames, and Semantics method.Semantic: frame semantic parsing (Das et al., 2014) is aimed to extract frame-specific predicate-argument structures from sentences[3].
+Syntax: given each candidate answer, we attempt to transform the question to a statement using the extraction rules[4]. We could see figure 2 for sematic and figure 3 for syntax.
+\begin{figure}[p]
+	\centering
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=1\linewidth]{../sematic.png}
+		\caption{ROC}
+		\label{figure 2:sematic parsing}
+	\end{subfigure}
+
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=1\linewidth]{../syntax.png}
+		\caption{ROC}
+		\label{figure 3:syntax}
+	\end{subfigure}
+
+\end{figure}
+
 But according to the error analysis suggests that deeper linguistic analysis and inferential reasoning can yield further improvements on this task.
 
-\subsubsection*{ Comprehension with Discourse Relations[5]}
-The model jointly identifies relevant sentences, establishes relations between them and predicts an answer.
+Comprehension with Discourse Relations[5].The model jointly identifies relevant sentences, establishes relations between them and predicts an answer.
 The key idea is to implant discourse analysis into a joint model for comprehension.
-And the drawback of this model is that the accuracy varies significantly according to the question type.
+As we could see in picture 4.And the drawback of this model is that the accuracy varies significantly according to the question type.
 Which means not really stable.
+\begin{figure}[p]
+	\centering
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=1\linewidth]{../disclosure.png}
+		\caption{ROC}
+		\label{figure 4:disclosure method}
+	\end{subfigure}
 
-\subsubsection*{  Comprehension for Learning Answer-Entailing Structures[6]}
-We posit that there is a hidden (latent) structure that explains the relation between the question, correct answer, and text.
+\end{figure}
+
+Comprehension for Learning Answer-Entailing Structures[6].We posit that there is a hidden (latent) structure that explains the relation between the question, correct answer, and text.
 For this given structure, the correctness of the answer is evident.
@@
 Firstly, we should presents a unified max-margin framework that learns to find these hidden structures (given a corpus of question-answer pairs), and then uses what it learns to answer machine comprehension questions on novel texts.
+We could see this from figure 5.
 But the drawback of this method is that since inference is cheaply modelled via alignment structure, we lack the ability to deeply reason about facts or numbers.
+\begin{figure}[p]
+	\centering
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=1\linewidth]{../disclosure.png}
+		\caption{ROC}
+		\label{figure 5:answer entailing method}
+	\end{subfigure}
+
+\end{figure}
 
 \section{Research for Neural Network}
+Firstly, some basic concept for RNN and ANN.In machine learning and cognitive science, artificial neural networks (ANNs) are a family of models inspired by biological neural networks (the central nervous systems of animals, in particular the brain) and are used to estimate or approximate functions that can depend on a large number of inputs and are generally unknown.
+Artificial neural networks are generally presented as systems of interconnected 'neurons' which exchange messages between each other.
+An ANN is typically defined by three types of parameters:
+The interconnection pattern between the different layers of neurons
+The learning process for updating the weights of the interconnections
+The activation function that converts a neuron's weighted input to its output activation.
+Contrary to feedforward networks, recurrent neural networks (RNNs) are models with bi-directional data flow.
+While a feedforward network propagates data linearly from input to output, RNNs also propagate data from later processing stages to earlier stages.
+RNNs can be used as general sequence processors.
+For RNN model, there are several types, like Fully recurrent network, Hopfield network, Elman networks and Jordan networks, Echo state network and Long short term memory network,etc.
 
-\subsubsection*{Deep LSTM Reader Model}
+The Long short term memory (LSTM) network, developed by Hochreiter and Schmidhuber in 1997[7] is an artificial neural network structure that unlike traditional RNNs doesn't have the vanishing gradient problem (compare the section on training algorithms below).
+It works even when there are long delays, and it can handle signals that have a mix of low and high frequency components.
+LSTM RNN outperformed other methods in numerous applications such as language learning[8] and connected handwriting recognition[9].
+
 The Deep LSTM Reader embed long sequences into a vector representation which contains enough information to generate a full translation in another language.
@@
 So this one is the old version of neural networking.
+We could see from figure 6 for LSTM.
 
-\subsubsection*{Impatient Reader Model}
+\begin{figure}[p]
+	\centering
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=1\linewidth]{../LSTM.png}
+		\caption{ROC}
+		\label{figure 6:LSTM}
+	\end{subfigure}
+
+\end{figure}
+
 The Impatient Reader focuses on the passages of a context document that are most likely to inform the answer to the query.
@@
 The result is an attention mechanism that allows the model to recurrently accumulate information from the document as it sees each query token, ultimately outputting a final joint document query representation for the answer prediction.
+We could see figure 7 for impatient reader.
+\begin{figure}[p]
+	\centering
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=1\linewidth]{../impa.png}
+		\caption{ROC}
+		\label{figure 7:impatient reader}
+	\end{subfigure}
 
-\subsubsection*{Attentive Reader Model}
+\end{figure}
+
 The Attentive Reader can be viewed as a generalization of the application of Memory Networks to question answering.
@@
 Although this method cannot be backwards checking as impatient reader but according to some article, these two methods have the similar results, so our group used this model.
+We could see figure 8 for attentive model.
+\begin{figure}[p]
+	\centering
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=1\linewidth]{../attentive.png}
+		\caption{ROC}
+		\label{figure 8:attentive model}
+	\end{subfigure}
+
+\end{figure}
 
@@
 For deep learning part, we use blocks and fuels, Theano framework for deep learning part. 
+Blocks and fuel[10] are two Python frameworks to train neural networks on large datasets.
+Blocks is based on Theano, a linear algebra compiler with CUDA-support (Bastien et al., 2012; Bergstra et al., 2010).
+It facilitates the training of complex neural network models by providing parametrized Theano operations, attaching metadata to Theano symbolic computational graph, and providing an extensive set of utilities to assist training the networks, e.g.
+training algorithms, logging, monitoring, visualization, and serialization.
+Fuel provides a standard format for machine learning datasets.
+It allows the user to easily iterate over large datasets, performing many types of pre-processing on the fly[10].
+Blocks and Fuel are being developed by the Montreal Institute of Learning Algorithms (MILA) at the University of Montreal. Their focus lies on quick prototyping of complex neural network models. 
+Instead of introducing new abstract objects representing 'models' or 'layers'.
+Blocks annotates the theano computational graph, maintaining the flexibility of theano while making large models manageable.
+Data processing is an integral part of training neural networks, which is not addressed by many of the aforementioned frameworks.
+Fuel aims to fill this gap.
+It provides tools to download datasets and iterate/preprocess them efficiently.
+
+Theano is a popular choice for the implementation of neural networks (see e.g.
+Goodfellow et al.
+(2013b); Pascanu et al.
+(2013)).
+Blocks and many other libraries, such as Pylearn2 (Goodfellow et al., 2013a), build on Theano by providing reusable components that are common in neural networks, such as linear transformations followed by non-linear activations, or more complicated components such as LSTM units.
+In Blocks these components are referred to as 'bricks' or 'parametrized Theano operations'.
+Blocks comes with a large number of 'bricks'. 
+The gradient descent training algorithm in Blocks is composed of different 'step rules' that modify the descent direction (learning rate scaling, momentum, gradient clipping, weight norm clipping, etc.).
+A variety of algorithms such as AdaGrad, ADADELTA, Adam, RMSProp are available as step rules.
+But in our project, we use gradient descent algorithm.
+The goal of fuel is to provide a common interface to a variety of data formats and published datasets such as MNIST, CIFAR-10, ImageNet, etc.
+while making it easy for users to write an interface to new datasets.
+Blocks relies on Fuel for its data interface, but Fuel can easily be used by other machine learning frameworks that interface with datasets. 
+Fuel offers built-in scripts that automate the task of downloading datasets, (similar to e.g. skdata1) and converting them to Fuel HDF5 specification. 
+The fuel download script is used to download raw data files.
+Downloading the raw MNIST data files is as easy as typing fuel download mnist.
+The fuel convert script is used to convert raw data files into HDF5-format.
+Reproducibility being an important feature of both Fuel and Blocks, the fuel convert script automatically tags all files it creates with relevant module and interface versions and the exact command that was used to generate these files.
+Inspection of this metadata is done with the fuel info script.
+Theano is a compiler for mathematical expressions in Python that combines the convenience of NumPy syntax with the speed of optimized native machine language.
+The user composes mathematical expressions in a high-level description that mimics NumPy syntax and semantics, while being statically typed and functional (as opposed to imperative).
+These expressions allow Theano to provide symbolic differentiation.
+[11]
+Theano was introduced to the machine learning community by Bergstra et al.
+(2010) as a CPU and GPU mathematical compiler, demonstrating how it can be used to symbolically define mathematical functions, automatically derive gradient expressions, and compile these expressions into executable functions that outperform implementations using other existing tools[12].
+\section{compare of original method and the method we used}
+The Attentive Reader can be viewed as a generalisation of the application of Memory Networks to question answering.
+That model employs an attention mechanism at the sentence level where each sentence is represented by a bag of embeddings.
+The Attentive Reader employs a finer grained token level attention mechanism where the tokens are embedded given their entire future and past context in the input document.
+The representation r of the document d is formed by a weighted sum of these output vectors.
+These weights are interpreted as the degree to which the network attends to a particular token in the document.
+Given this attention score the embedding of the document r is computed as the weighted sum of the token embeddings.
+
+According to a recent google paper, for the Deep LSTM Reader, they consider hidden layer sizes [64, 128, 256], depths [1, 2, 4], initial learning rates [1E3, 5E4, 1E4, 5E5], batch sizes [16, 32] and dropout [0.0, 0.1, 0.2].
+Evaluated two types of feeds.
+In the cqa setup they feed first the context document and subsequently the question into the encoder, while the qca model starts by feeding in the question followed by the context document.
+For the attention models they consider hidden layer sizes [64, 128, 256], single layer, initial learning rates [1E4, 5E5, 2.5E5, 1E5], batch sizes [8, 16, 32] and dropout [0, 0.1, 0.2, 0.5].
+For all models we used asynchronous RmsProp [20] with a momentum of 0.9 and a decay of 0.95.
+
+We define a new method to determine which possible answer is the correct one.
+(function) That is, the correct answer should be the most similar to the most highly attended words in the story.
+We use the similarity metric (function) for a multiple choice answer of length n words.
+Take the weighted average of the attention each word from the multiple choice answer has within the story.
+If a word in the answer is not in the story, we then chooce to use word distance from the closest attended word as apenalty.
+
+\section{run time}
+As for the run time, and computational complexity. Original Attentive Reader: trained for 2-4 days using two NVIDIA Titan Black GPUs (PassMark score 8,667 each)
+Our setup: one NVIDIA GTX 660 GPU (PassMark score 4,120) inside older machine: Core 2 Quad Q8300, 8GB DDR2 PC6400 RAM. And the training time is around one day.
+For result, we first calculate weight matrix multiply vector embedding matrix for each word, and choose the highest possibility. The higher the possibility it is, the more colorful the words could be.
 
@@
 For preprocessing part, we firstly setup the NLTK working environment with python and later import some libraries like stem, tokenize, corpus, etc.
-We deal with deleting punctuation like “,” “.”,etc.
-Later we also extract questions pattern like “when”, “how”, etc.
+We deal with deleting punctuation like ',' '.',etc.
+Later we also extract questions pattern like 'when', 'how', etc.
 we change numbers into English words by dictionary.
@@
 	\item using lemmatizatio: Returns the input word unchanged if it cannot be found in WordNet.
-	\item dealing with rawfile and answer file input. To become like…
+	\item dealing with rawfile and answer file input. To become,
 	\item getting the entities.
@@
 \section{Results, performance evaluation, and analysis}
+
+\begin{tabular}
+	{l*{2}{c}r}   	 Method  & MCTest Accuracy  \\ \hline
+	Baseline (sliding window + word distance) & 57.75 \\ 
+	Learning Answer-Entailing Structures for Machine Comprehension (Sachan et. al, 2015) & 67.83\\
+	Machine Comprehension with Discourse Relations (Narasimhan et. al, 2015) & 63.75\\
+	Machine Comprehension with Syntax, Frames and Symantics (Wang et. al, 2015) & 69.94\\
+	Our Method & ???\\
+
+\end{tabular}
 
@@
 In the bibliography, use \texttt{\textbackslash textsuperscript} for ``st'', ``nd'', ...:
-E.g., \enquote{The 2\textsuperscript{nd} conference on examples}.
+E.g., \enquote{The 2\textsuperscript{nd} conference on examples}. \cite{richardson2013mctest}
 When you use \href{http://www.jabref.org}{JabRef}, you can use the clean up command to achieve that.
@@
 
-All links were last followed on October 5, 2014.
+%All links were last followed on October 5, 2014.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-04-02 project report/LNCS-template/paper.tex
report latest version

@@
 		\centering
-		\includegraphics[width=1\linewidth]{../parsing.png}
+		\includegraphics[width=1\linewidth]{../pic/parsing.png}
 		\caption{ROC}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{../sematic.png}
+		\includegraphics[width=1\linewidth]{../pic/sematic.png}
 		\caption{ROC}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{../syntax.png}
+		\includegraphics[width=1\linewidth]{../pic/syntax.png}
 		\caption{ROC}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{../disclosure.png}
+		\includegraphics[width=1\linewidth]{../pic/disclosure.png}
 		\caption{ROC}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{../LSTM.png}
+		\includegraphics[width=1\linewidth]{../pic/LSTM.png}
 		\caption{ROC}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{../impa.png}
+		\includegraphics[width=1\linewidth]{../pic/impa.png}
 		\caption{ROC}
@@
 		\centering
-		\includegraphics[width=1\linewidth]{../attentive.png}
+		\includegraphics[width=1\linewidth]{../pic/attentive.png}
 		\caption{ROC}
@@
 \section{compare of original method and the method we used}
+For preprocessing part:
+1) split the story dataset into one story one file, and do the same thing on the related answer dataset 
+2) label correct answers obtained from corresponding answer file
+in each story file 
+3) convert ‘n’t’ to ‘not’ using Regular Expression and numbers to words using a recrusive function implemented by ourselves on story, questions and answers in each story file 
+4) lowercase all text of stories, tokenize them, then build a vocabulary file without repeat words
+5) find out entities in each story and replace them with entity identifiers, then add the corresponding entity and entity identifier list below the questions
+6) delete punctuations on the text of each story, the reason for doing this after step 5 is that punctuations will help to identify the entities 
+7) remove stop words, lemmatization and stemming on each story dealing with NLTK library functions
+8) preprocess both questions and answers using the entity list gained from step 5
+
 The Attentive Reader can be viewed as a generalisation of the application of Memory Networks to question answering.

### 2016-04-03 Proposal/ProjectProposal.tex
proposal

\documentclass[]{scrartcl}

\usepackage{geometry}
\geometry{legalpaper, margin=1.6in}

%opening
\title{ECE 657A Project Proposal}
\author{Huang Tianhui (20587328), Laura McCrackin (20262085), \\
and Yuzhou Wang (20609396)}

\begin{document}

\maketitle

\section{Problem Overview}

One of the most important and intriguing problems in the field of Natural Language Processing (NLP) is that of extracting meaning from a passage of text.  A human reader is able to comprehend the main ideas from a piece of writing despite the many inherent subtleties of the medium; not only do sentence structures and descriptive language have considerable variation, but the same words are often used differently depending on their context.

In our project, we will be working with question answering using the Machine Comprehension Test (MCTest) dataset created by Microsoft \cite{richardson2013mctest}.  This dataset consists of 500 stories, each between 150 and 300 words and intended to be at a grade 1-4 reading level, along with four reading comprehension questions and answers per story.  As each story is fictional, the answers can only be found in the story itself, which requires high-level machine comprehension without any world knowledge. The answers to most questions are non-trivial, and must be derived from at least two sentences within the text. Our main goal is to implement an algorithm that is capable of answering these questions with a high degree of accuracy.

\section{Prior Work}
Many different approaches have been used for natural language processing. Traditionally, a pipeline of NLP models has been used for attempting question answering, using models that make heavy use of linguistic annotation, structured world knowledge and semantic parsing.

Hai Wang et al. proposed a framework to implement a series of heuristics to handle many of the different cases in the question answering task \cite{wang2015machine}.  They focused on combining novel features of dependency syntax, frame semantics, co-reference resolution and word embeddings with a number of baseline features. Their empirical results demonstrate that the use of linguistic structure plays a significant role in machine comprehension.

On the other hand, Hermann et al. described a series of attention-based deep neural networks, which rely on only a minimal understanding of language structure to predict which token in the text passage contains the answer to each question.  They demonstrate the limitations of the simplest question answering methods, such as finding the minimum distance between candidate words, and show that their method's ability to handle semantic information over longer distances provides much stronger performance when answering questions about news articles \cite{NIPS2015}.

Researchers at Carnegie Mellon University and Microsoft recently proposed a method for modelling pieces of text using a latent structural SVM in what they call an answer-entailing structure, so that the answers to questions may be more easily inferred \cite{sachan2015learning}.

\section{Proposed Approach}
Building on previous approaches, we plan to create a hybrid method for performing question answering.  Our method will begin with a series of heuristic approaches – for instance, checking for word distances, and beginning as Sachan et al. with a simple classification step performed on each question, using the question words (ex. ``who''/``what''/``where'') to determine the type of response expected.  Questions for which we can obtain a high confidence measure may be solved entirely using these heuristics (for instance, if all key words are found in a single, simple sentence in the passage).

For more complicated cases, we plan to use a deep learning method similar to the Attentive Reader and Impatient Reader models proposed by Hermann et al.

As we develop our method, we will work with a series of simplified test cases to benchmark each step.  For instance, we can first test the accuracy of individual heuristics on only questions with answers derived from a single sentence, and add in the remaining test cases as we verify each step.

\section{Challenges}
This problem is a difficult one that poses many unique challenges.  Firstly, our dataset is comprised of human-written stories that may contain errors, stylistic inconsistencies, and many linguistic corner cases, and it is likely that many of these cannot reasonably be corrected or accounted for.  Furthermore, we may need to experiment with several different heuristic approaches and attentional models to create a hybrid model with strong performance.

That being said, this is an exciting and relatively young area of research -- with many interesting articles being released just this past year -- and we are looking forward to the challenges it entails.

\bibliographystyle{IEEEbib}
\bibliography{refs}

\end{document}

### 2016-04-03 Proposal/refs.bib.tex
proposal

@incollection{NIPS2015_5945,
author = {Hermann, Karl Moritz and Kocisky, Tomas and Grefenstette, Edward and Espeholt, Lasse and Kay, Will and Suleyman, Mustafa and Blunsom, Phil},
booktitle = {Advances in Neural Information Processing Systems 28},
editor = {Cortes, C and Lawrence, N D and Lee, D D and Sugiyama, M and Garnett, R},
pages = {1684--1692},
publisher = {Curran Associates, Inc.},
title = {{Teaching Machines to Read and Comprehend}},
url = {http://papers.nips.cc/paper/5945-teaching-machines-to-read-and-comprehend.pdf},
year = {2015}
}

### 2016-04-04 project report/LNCS-template/paper.tex
report

--- 2016-04-02 project report/LNCS-template/paper.tex
@@
 %Single insitute
-\author{Laura McCrackin (20262085),Yuzhou Wang (20609396) \and Tianhui Huang (20587328)}
+\author{Laura McCrackin (20262085),  Tianhui Huang (20587328) \and Yuzhou Wang (20609396)}
 %If there are too many authors, use \authorrunning
@@
 The authors of stories are all workers, residing in the United States.
-The average worker is 36 years old, more educated than the United States population in general (Paolacci et al., 2010), and the majority of workers are female.
-Workers were instructed to write a short (150-300 words) fictional story, and to write as if for a child in grade school.
+The average worker is 36 years old, more educated than the United States population in general, and the majority of workers are female.
+Workers were instructed to write a short fictional story, and to write as if for a child in grade school.
 Workers were also asked to provide four reading comprehension questions pertaining to their story and, for each, four multiple-choice answers.
@@
 		\centering
-		\includegraphics[width=1\linewidth]{../parsing.png}
-		\caption{ROC}
+		\includegraphics[width=1\linewidth]{../pic/parsing.png}
+
 		\label{figure 1:Frame-Semantic Parsing}
 	\end{subfigure}	
+\end{figure}
 
-\end{figure}
+%\begin{figure}[p]
+%	\centering
+%	\begin{subfigure}{.5\textwidth}
+%		\centering
+%		\includegraphics[width=1\linewidth]{../images-update/1-(3)-2.png}
+%		\caption{ROC}
+%		\label{fig:sub1}
+%	\end{subfigure}
+
+%\end{figure}
 
@@
 
-Other people also have the idea of comprehension with Syntax, Frames, and Semantics method.Semantic: frame semantic parsing (Das et al., 2014) is aimed to extract frame-specific predicate-argument structures from sentences[3].
+Other people also have the idea of comprehension with Syntax, Frames, and Semantics method.Semantic: frame semantic parsing is aimed to extract frame-specific predicate-argument structures from sentences[3].
 Syntax: given each candidate answer, we attempt to transform the question to a statement using the extraction rules[4]. We could see figure 2 for sematic and figure 3 for syntax.
-\begin{figure}[p]
-	\centering
-	\begin{subfigure}{.5\textwidth}
-		\centering
-		\includegraphics[width=1\linewidth]{../sematic.png}
-		\caption{ROC}
-		\label{figure 2:sematic parsing}
-	\end{subfigure}
+%\begin{figure}[p]
+%	\centering
+%	\begin{subfigure}{.5\textwidth}
+%		\centering
+%		\includegraphics[width=1\linewidth]{../pic/sematic.png}
+%		\caption{ROC}
+%		\label{figure 2:sematic parsing}
+%	\end{subfigure}
 
-\end{figure}
+%\end{figure}
 
-\begin{figure}[p]
-	\centering
-	\begin{subfigure}{.5\textwidth}
-		\centering
-		\includegraphics[width=1\linewidth]{../syntax.png}
-		\caption{ROC}
-		\label{figure 3:syntax}
-	\end{subfigure}
-
-\end{figure}
+%\begin{figure}[p]
+%	\centering
+%	\begin{subfigure}{.5\textwidth}
+%		\centering
+%		\includegraphics[width=1\linewidth]{../pic/syntax.png}
+%		\caption{ROC}
+%		\label{figure 3:syntax}
+%	\end{subfigure}	
+%\end{figure}
 
@@
 Which means not really stable.
-\begin{figure}[p]
-	\centering
-	\begin{subfigure}{.5\textwidth}
-		\centering
-		\includegraphics[width=1\linewidth]{../disclosure.png}
-		\caption{ROC}
-		\label{figure 4:disclosure method}
-	\end{subfigure}
-
-\end{figure}
+%\begin{figure}[p]
+%	\centering
+%	\begin{subfigure}{.5\textwidth}
+%		\centering
+%		\includegraphics[width=1\linewidth]{../pic/disclosure.png}
+%		\caption{ROC}
+%		\label{figure 4:disclosure method}
+%	\end{subfigure}
+%\end{figure}
 
@@
 But the drawback of this method is that since inference is cheaply modelled via alignment structure, we lack the ability to deeply reason about facts or numbers.
-\begin{figure}[p]
-	\centering
-	\begin{subfigure}{.5\textwidth}
-		\centering
-		\includegraphics[width=1\linewidth]{../disclosure.png}
-		\caption{ROC}
-		\label{figure 5:answer entailing method}
-	\end{subfigure}
-
-\end{figure}
+%\begin{figure}[p]
+%	\centering
+%	\begin{subfigure}{.5\textwidth}
+%		\centering
+%		\includegraphics[width=1\linewidth]{../pic/disclosure.png}
+%		\caption{ROC}
+%		\label{figure 5:answer entailing method}
+%	\end{subfigure}
+%\end{figure}
 
@@
 
-\begin{figure}[p]
-	\centering
-	\begin{subfigure}{.5\textwidth}
-		\centering
-		\includegraphics[width=1\linewidth]{../LSTM.png}
-		\caption{ROC}
-		\label{figure 6:LSTM}
-	\end{subfigure}
-
-\end{figure}
+%\begin{figure}[p]
+%	\centering
+%	\begin{subfigure}{.5\textwidth}
+%		\centering
+%		\includegraphics[width=1\linewidth]{../pic/LSTM.png}
+%		\caption{ROC}
+%		\label{figure 6:LSTM}
+%	\end{subfigure}
+%\end{figure}
 
@@
 We could see figure 7 for impatient reader.
-\begin{figure}[p]
-	\centering
-	\begin{subfigure}{.5\textwidth}
-		\centering
-		\includegraphics[width=1\linewidth]{../impa.png}
-		\caption{ROC}
-		\label{figure 7:impatient reader}
-	\end{subfigure}
-
-\end{figure}
+%\begin{figure}[p]
+%	\begin{subfigure}{.5\textwidth}
+%		\centering
+%		\includegraphics[width=1\linewidth]{../pic/impa.png}
+%		\caption{ROC}
+%		\label{figure 7:impatient reader}
+%	\end{subfigure}
+%\end{figure}
 
@@
 We could see figure 8 for attentive model.
-\begin{figure}[p]
-	\centering
-	\begin{subfigure}{.5\textwidth}
-		\centering
-		\includegraphics[width=1\linewidth]{../attentive.png}
-		\caption{ROC}
-		\label{figure 8:attentive model}
-	\end{subfigure}
-
-\end{figure}
+%\begin{figure}[p]
+%	\centering
+%	\begin{subfigure}{.5\textwidth}
+%		\centering
+%		\includegraphics[width=1\linewidth]{../pic/attentive.png}
+%		\caption{ROC}
+%		\label{figure 8:attentive model}
+%	\end{subfigure}	
+%\end{figure}
 
@@
 Blocks and fuel[10] are two Python frameworks to train neural networks on large datasets.
-Blocks is based on Theano, a linear algebra compiler with CUDA-support (Bastien et al., 2012; Bergstra et al., 2010).
+Blocks is based on Theano, a linear algebra compiler with CUDA-support.
 It facilitates the training of complex neural network models by providing parametrized Theano operations, attaching metadata to Theano symbolic computational graph, and providing an extensive set of utilities to assist training the networks, e.g.
@@
 
-Theano is a popular choice for the implementation of neural networks (see e.g.
-Goodfellow et al.
-(2013b); Pascanu et al.
-(2013)).
-Blocks and many other libraries, such as Pylearn2 (Goodfellow et al., 2013a), build on Theano by providing reusable components that are common in neural networks, such as linear transformations followed by non-linear activations, or more complicated components such as LSTM units.
+Theano is a popular choice for the implementation of neural networks.
+Blocks and many other libraries, such as Pylearn2, build on Theano by providing reusable components that are common in neural networks, such as linear transformations followed by non-linear activations, or more complicated components such as LSTM units.
 In Blocks these components are referred to as 'bricks' or 'parametrized Theano operations'.
@@
 The user composes mathematical expressions in a high-level description that mimics NumPy syntax and semantics, while being statically typed and functional (as opposed to imperative).
-These expressions allow Theano to provide symbolic differentiation.
-[11]
-Theano was introduced to the machine learning community by Bergstra et al.
-(2010) as a CPU and GPU mathematical compiler, demonstrating how it can be used to symbolically define mathematical functions, automatically derive gradient expressions, and compile these expressions into executable functions that outperform implementations using other existing tools[12].
+These expressions allow Theano to provide symbolic differentiation[11].
+Theano was introduced to the machine learning community as a CPU and GPU mathematical compiler, demonstrating how it can be used to symbolically define mathematical functions, automatically derive gradient expressions, and compile these expressions into executable functions that outperform implementations using other existing tools[12].
 \section{compare of original method and the method we used}
+For preprocessing part:
+1) split the story dataset into one story one file, and do the same thing on the related answer dataset 
+2) label correct answers obtained from corresponding answer file
+in each story file 
+3) convert abbreviation using Regular Expression and numbers to words using a recrusive function implemented by ourselves on story, questions and answers in each story file 
+4) lowercase all text of stories, tokenize them, then build a vocabulary file without repeat words
+5) find out entities in each story and replace them with entity identifiers, then add the corresponding entity and entity identifier list below the questions
+6) delete punctuations on the text of each story, the reason for doing this after step 5 is that punctuations will help to identify the entities 
+7) remove stop words, lemmatization and stemming on each story dealing with NLTK library functions
+8) preprocess both questions and answers using the entity list gained from step 5
+
 The Attentive Reader can be viewed as a generalisation of the application of Memory Networks to question answering.
@@
 
-We define a new method to determine which possible answer is the correct one.
-(function) That is, the correct answer should be the most similar to the most highly attended words in the story.
-We use the similarity metric (function) for a multiple choice answer of length n words.
+For deep mind model output, we define function 1,for a given document(d) and query(q), we could estimate the probability of word a being the correct answer.We define a new method to determine which possible answer is the correct one.
+As we could see from function 2, that is, the correct answer should be the most similar to the most highly attended words in the story.
+We use the similarity metric, as we could see from function 3.
+For a multiple choice answer of length n words.
 Take the weighted average of the attention each word from the multiple choice answer has within the story.
-If a word in the answer is not in the story, we then chooce to use word distance from the closest attended word as apenalty.
-
+If a word in the answer is not in the story, we then chooce to use word distance from the closest attended word as apenalty.\newline
+Function 1: \newline
+ here some error for the function
+%p(a|d,q) \propto exp (W(a) g(d,q)), a \epsilon V
+W stands for weight, g stands for vector embedding and v stands for vocabulary \newline
+Function 2: \newline
+C=max[S(Ci,p(a|d,q))] \newline
+here C is for correct choice, S is for similarity, Ci is for ith multiple choice answer, i from 1 to 4.
+\newline
+Function 3:\newline
+%S(Ci,p(a|d,q))=\sum_{j=1}^{n} p(aj|d,q)/n    
+here still a small problem and did not figure out yet
+%S(Ci,p(a|d,q))=\sigma p(aj|d,q)/n
+%%%%%%%
 \section{run time}
 As for the run time, and computational complexity. Original Attentive Reader: trained for 2-4 days using two NVIDIA Titan Black GPUs (PassMark score 8,667 each)
-Our setup: one NVIDIA GTX 660 GPU (PassMark score 4,120) inside older machine: Core 2 Quad Q8300, 8GB DDR2 PC6400 RAM. And the training time is around one day.
+Our setup: one NVIDIA GTX 660 GPU  inside older machine: Core 2 Quad Q8300, 8GB DDR2 PC6400 RAM. And the training time is around one day.
 For result, we first calculate weight matrix multiply vector embedding matrix for each word, and choose the highest possibility. The higher the possibility it is, the more colorful the words could be.
@@
 
-\begin{inparaenum}
-	\item using stop words library to remove stop words
-	\item using regular expression
-	\item define a function and by recursion to convert a number into a verb
-	\item using library to deal with stem words
-	\item using lemmatizatio: Returns the input word unchanged if it cannot be found in WordNet.
-	\item dealing with rawfile and answer file input. To become,
-	\item getting the entities.
-	\item preprocessing both questions and answers
-\end{inparaenum}
+1) split the story dataset into one story one file, and do the same thing on the related answer dataset 
+2) label correct answers obtained from corresponding answer file
+in each story file 
+3) convert abbreviation using Regular Expression and numbers to words using a recrusive function implemented by ourselves on story, questions and answers in each story file 
+4) lowercase all text of stories, tokenize them, then build a vocabulary file without repeat words
+5) find out entities in each story and replace them with entity identifiers, then add the corresponding entity and entity identifier list below the questions
+6) delete punctuations on the text of each story, the reason for doing this after step 5 is that punctuations will help to identify the entities 
+7) remove stop words, lemmatization and stemming on each story dealing with NLTK library functions
+8) preprocess both questions and answers using the entity list gained from step 5
 
@@
 
-Brackets work as designed:
-<test>
-
-The symbol for powerset is now correct: $\powerset$ and not a Weierstrass p ($\wp$).
-
-\begin{inparaenum}
-\item All these items...
-\item ...appear in one line
-\item This is enabled by the paralist package.
-\end{inparaenum}
-
-``something in quotes'' using plain tex or use \enquote{the enquote command}.
-
 \section{Conclusion and Outlook}
@@
 \subsubsection*{Acknowledgments}
-...
 
-In the bibliography, use \texttt{\textbackslash textsuperscript} for ``st'', ``nd'', ...:
-E.g., \enquote{The 2\textsuperscript{nd} conference on examples}. \cite{richardson2013mctest}
-When you use \href{http://www.jabref.org}{JabRef}, you can use the clean up command to achieve that.
+%In the bibliography, use \texttt{\textbackslash textsuperscript} for ``st'', ``nd'', ...:
+%E.g., \enquote{The 2\textsuperscript{nd} conference on examples}. 
+%When you use \href{http://www.jabref.org}{JabRef}, you can use the clean up command to achieve that.
 
+\cite{richardson2013mctest}
+\cite{hermann2015teaching}
+\cite{wang2015machine}
+\cite{yao2013answer}
+\cite{narasimhan2015machine}
+\cite{sachan2015learning}
+\cite{hochreiter1997long}
+\cite{gers2001lstm}
+\cite{graves2009offline}
+\cite{van2015blocks}
+\cite{bergstra2010theano}
+\cite{bastien2012theano}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%All links were last followed on October 5, 2014.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%% template for figure and table
-\begin{figure}
-	Simple Figure
-	\caption{ Figure}
-	\label{fig:simple}
-\end{figure}
-
-\begin{table}
-	\caption{Simple Table}
-
-	\label{tab:simple}
-	Simple Table
-\end{table}
-%%%%%%%%%%%%%%%%%%
-cref Demonstration: Cref at beginning of sentence, cref in all other cases.
-
-\Cref{fig:simple} shows a simple fact, although \cref{fig:simple} could also show something else.
-
-\Cref{tab:simple} shows a simple fact, although \cref{tab:simple} could also show something else.
-
-\Cref{sec:intro} shows a simple fact, although \cref{sec:intro} could also show something else.
+%\Cref{fig:simple} shows a simple fact, although \cref{fig:simple} could also show something else.
+%\Cref{tab:simple} shows a simple fact, although \cref{tab:simple} could also show something else.
+%\Cref{sec:intro} shows a simple fact, although \cref{sec:intro} could also show something else.
 %%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-04-04 DeepMind-Teaching-Machines-to-Read-and-Comprehend/data.py
Merging in Attentive Reader stuff, based off repo by thomasmesnard. Added functionality to load saved model, recreate computation graph, load in test stream, find output probabilities of each, and save to file. Also added theanotest.py, test run for changing error/answer calc functionality.

@@ -1,0 +1,180 @@
+import logging
+import random
+import numpy
+
+import cPickle
+
+from picklable_itertools import iter_
+
+from fuel.datasets import Dataset
+from fuel.streams import DataStream
+from fuel.schemes import IterationScheme, ConstantScheme
+from fuel.transformers import Batch, Mapping, SortMapping, Unpack, Padding, Transformer
+
+import sys
+import os
+
+logging.basicConfig(level='INFO')
+logger = logging.getLogger(__name__)
+
+class QADataset(Dataset):
+    def __init__(self, path, vocab_file, n_entities, need_sep_token, **kwargs):
+        self.provides_sources = ('context', 'question', 'answer', 'candidates')
+
+        self.path = path
+
+        self.vocab = ['@entity%d' % i for i in range(n_entities)] + \
+                     [w.rstrip('\n') for w in open(vocab_file)] + \
+                     ['<UNK>', '@placeholder'] + \
+                     (['<SEP>'] if need_sep_token else [])
+
+        self.n_entities = n_entities
+        print self.n_entities
+        self.vocab_size = len(self.vocab)
+        print self.vocab_size
+        self.reverse_vocab = {w: i for i, w in enumerate(self.vocab)}
+        #print self.reverse_vocab{1}
+        super(QADataset, self).__init__(**kwargs)
+
+    def to_word_id(self, w, cand_mapping):
+        if w in cand_mapping:
+            #print  cand_mapping[w]
+            return cand_mapping[w]
+        elif w[:7] == '@entity':
+            raise ValueError("Unmapped entity token: %s"%w)
+        elif w in self.reverse_vocab:
+            return self.reverse_vocab[w]
+        else:
+            return self.reverse_vocab['<UNK>']
+
+    def to_word_ids(self, s, cand_mapping):
+        return numpy.array([self.to_word_id(x, cand_mapping) for x in s.split(' ')], dtype=numpy.int32)
+
+    def get_data(self, state=None, request=None):
+        if request is None or state is not None:
+            raise ValueError("Expected a request (name of a question file) and no state.")
+
+        lines = [l.rstrip('\n') for l in open(os.path.join(self.path, request))]
+        #print lines
+        ctx = lines[2]
+        q = lines[4]
+        a = lines[6]
+        cand = [s.split(':')[0] for s in lines[8:]]
+
+        entities = range(self.n_entities)
+        while len(cand) > len(entities):
[…]

### 2016-04-04 DeepMind-Teaching-Machines-to-Read-and-Comprehend/model/attentive_reader.py

@@ -1,0 +1,166 @@
+import theano
+from theano import tensor
+import numpy
+
+from blocks.bricks import Tanh, Softmax, Linear, MLP, Identity, Rectifier
+from blocks.bricks.lookup import LookupTable
+from blocks.bricks.recurrent import LSTM
+
+from blocks.filter import VariableFilter
+from blocks.roles import WEIGHT
+from blocks.graph import ComputationGraph, apply_dropout, apply_noise
+
+def make_bidir_lstm_stack(seq, seq_dim, mask, sizes, skip=True, name=''):
+    bricks = []
+
+    curr_dim = [seq_dim]
+    curr_hidden = [seq]
+
+    hidden_list = []
+    for k, dim in enumerate(sizes):
+        fwd_lstm_ins = [Linear(input_dim=d, output_dim=4*dim, name='%s_fwd_lstm_in_%d_%d'%(name,k,l)) for l, d in enumerate(curr_dim)]
+        fwd_lstm = LSTM(dim=dim, activation=Tanh(), name='%s_fwd_lstm_%d'%(name,k))
+
+        bwd_lstm_ins = [Linear(input_dim=d, output_dim=4*dim, name='%s_bwd_lstm_in_%d_%d'%(name,k,l)) for l, d in enumerate(curr_dim)]
+        bwd_lstm = LSTM(dim=dim, activation=Tanh(), name='%s_bwd_lstm_%d'%(name,k))
+
+        bricks = bricks + [fwd_lstm, bwd_lstm] + fwd_lstm_ins + bwd_lstm_ins
+
+        fwd_tmp = sum(x.apply(v) for x, v in zip(fwd_lstm_ins, curr_hidden))
+        bwd_tmp = sum(x.apply(v) for x, v in zip(bwd_lstm_ins, curr_hidden))
+        fwd_hidden, _ = fwd_lstm.apply(fwd_tmp, mask=mask)
+        bwd_hidden, _ = bwd_lstm.apply(bwd_tmp[::-1], mask=mask[::-1])
+        hidden_list = hidden_list + [fwd_hidden, bwd_hidden]
+        if skip:
+            curr_hidden = [seq, fwd_hidden, bwd_hidden[::-1]]
+            curr_dim = [seq_dim, dim, dim]
+        else:
+            curr_hidden = [fwd_hidden, bwd_hidden[::-1]]
+            curr_dim = [dim, dim]
+
+    return bricks, hidden_list
+
+class Model():
+    def __init__(self, config, vocab_size):
[…]

### 2016-04-04 DeepMind-Teaching-Machines-to-Read-and-Comprehend/paramsaveload.py

@@ -1,0 +1,44 @@
+import logging
+
+import numpy
+
+import cPickle
+
+from blocks.extensions import SimpleExtension
+
+logging.basicConfig(level='INFO')
+logger = logging.getLogger('extensions.SaveLoadParams')
+
+class SaveLoadParams(SimpleExtension):
+	def __init__(self, path, model, **kwargs):
+		super(SaveLoadParams, self).__init__(**kwargs)
+
+		self.path = path
+		self.model = model
+
+	def do_save(self):
+		with open(self.path, 'w') as f:
+			logger.info('Saving parameters to %s...'%self.path)
+			cPickle.dump(self.model.get_parameter_values(), f, protocol=cPickle.HIGHEST_PROTOCOL)
+
+	def do_load(self):
+		try:
+			with open(self.path, 'r') as f:
+				logger.info('Loading parameters from %s...'%self.path)
+				self.model.set_parameter_values(cPickle.load(f))
+				return True
+		except IOError:
+			pass
+			return False
+
+	def do(self, which_callback, *args):
+		if which_callback == 'before_training':
+			print "before training!\n"
+			if self.do_load():
+				print "success!"
+				self.after_training()
+		elif which_callback == 'after_training':
+			print "after training!\n"
+			# self.do_save()
+		else:
+			self.do_save()

### 2016-04-04 DeepMind-Teaching-Machines-to-Read-and-Comprehend/predict.py

@@ -1,0 +1,78 @@
+from collections import OrderedDict
+
+import numpy
+
+from blocks.extensions import SimpleExtension
+from blocks.graph import ComputationGraph
+
+
+class PredictDataStream(SimpleExtension):
+    """Evaluate tensors for a given datastream.
+
+    Parameters
+    ----------
+    data_stream : `~fuel.streams.DataStream`
+        Data stream for which to evaluate.
+    variables : list of `~theano.TensorVariable`
+        The variables to evaluate.
+    path : str, optional
+        The destination path for pickling. If not given, the output
+        will not be saved, but will be stored in the `prediction`
+        attribute instead.
+
+    Attributes
+    ----------
+    prediction : `collections.OrderedDict`
+        Storage for tensor evaluations. Maps tensor names to outputs
+        of type `numpy.ndarray`. If the callback has not been invoked,
+        this attribute is set to None.
+
+    """
+    def __init__(self, data_stream, variables, path=None, **kwargs):
+        self.data_stream = data_stream
+        self.variables = variables
+        # for zip(var, var1) in self.variables, variables
+        #     var.name = var1.name
+        #print (var.name for var in variables)
+        #print "varnames ^"
+        #self.variables.name = variables.name
+        self.path = path
+        self.prediction = None
+
+        kwargs.setdefault('after_training', True)
+        super(PredictDataStream, self).__init__(**kwargs)
+
+        cg = ComputationGraph(variables)
+        self.theano_function = cg.get_theano_function()
+
+    def do(self, which_callback, *args):
+        """Evaluate tensors for the given datastream."""
+        print self.variables
+
+        predictions = OrderedDict([(var.name, []) for var in self.variables])
+
+        print "---------------------\n"
+        print (var.name for var in self.variables)
+
+        for batch in self.data_stream.get_epoch_iterator(as_dict=True):
+            print batch
+            print "first\n"
+            prediction = self.theano_function(**batch)
+            print prediction
+            # theano.printing.debugprint(prediction)
+            for var, pred in zip(self.variables, prediction):
+
+                if var.name is None:
+                    var.name = "blah"
+                print "second: " + var.name + "\n"
+                predictions[var.name].append(pred)
+
+        print "third\n"
+        print predictions
+        # accumulate predictions for the entire epoch
+        # for var in self.variables:
+        #
+        #     predictions[var.name] = numpy.concatenate(predictions[var.name],
+        #                                               axis=0)
+        if self.path is not None:
+            numpy.savez(self.path, **predictions)

### 2016-04-04 DeepMind-Teaching-Machines-to-Read-and-Comprehend/test.py

@@ -1,0 +1,240 @@
+#!/usr/bin/env python
+
+import logging
+import numpy
+import sys
+import os
+import importlib
+import cPickle
+
+import theano
+from theano import tensor
+
+from blocks.extensions import Printing, SimpleExtension, FinishAfter, ProgressBar
+from blocks.extensions.monitoring import DataStreamMonitoring, TrainingDataMonitoring
+from blocks.graph import ComputationGraph
+from blocks.main_loop import MainLoop
+from blocks.model import Model
+from blocks.algorithms import GradientDescent
+from predict import PredictDataStream
+
+try:
+    from blocks.extras.extensions.plot import Plot
+    plot_avail = True
+except ImportError:
+    plot_avail = False
+    print "No plotting extension available."
+
+import data
+from paramsaveload import SaveLoadParams
+
+logging.basicConfig(level='INFO')
+logger = logging.getLogger(__name__)
+
+sys.setrecursionlimit(500000)
+
+if __name__ == "__main__":
+    if len(sys.argv) != 2:
+        print >> sys.stderr, 'Usage: %s config' % sys.argv[0]
+        sys.exit(1)
+    model_name = sys.argv[1]
+    config = importlib.import_module('.%s' % model_name, 'config')
+
+    # Build datastream
+    path = os.path.join(os.getenv("DATAPATH"), "deepmind-qa/cnn/questions/training")
+    valid_path = os.path.join(os.getenv("DATAPATH"), "deepmind-qa/cnn/questions/validation")
+    test_path = os.path.join(os.getenv("DATAPATH"), "deepmind-qa/cnn/questions/test")
+    vocab_path = os.path.join(os.getenv("DATAPATH"), "deepmind-qa/cnn/stats/training/vocab.txt")
+
+    ds, train_stream = data.setup_datastream(path, vocab_path, config)
+    # _, valid_stream = data.setup_datastream(valid_path, vocab_path, config)
+    _, test_stream = data.setup_datastream(test_path, vocab_path, config)
+
+    dump_path = os.path.join("model_params", model_name+".pkl")
+
+    # Build model
+    m = config.Model(config, ds.vocab_size)
+    # Build the Blocks stuff for training
+    model = Model(m.probs)#sgd_cost)
+    # model = Model(m.sgd_cost)
+    # print [v for l in m.monitor_vars for v in l]
+
+    print "new model:---------------------------------------------------------"
+    #print model.get_parameter_values()
+    try:
[…]

### 2016-04-04 DeepMind-Teaching-Machines-to-Read-and-Comprehend/theanotest.py

@@ -1,0 +1,54 @@
+import theano
+from theano import tensor
+import numpy
+from blocks.graph import ComputationGraph
+# x = tensor.arange(10)*10
+# s =  numpy.asarray([2, 8, 1], dtype=numpy.int32)
+#
+# # s =  numpy.asarray([2, 8, 1, 7, 7, 7, 7, 7, 7, 7], dtype=numpy.float32)
+# # test = tensor.eq(x, s)
+# # a = test.eval()
+# # print a
+# #xSub = theano.shared(x)
+# a = x[s].eval()
+# print a
+
+
+
+vocab = tensor.arange(10)
+probs = numpy.asarray([0, 0.8, 0, 0.2], dtype=numpy.float32)
+context = numpy.asarray([3, 2, 8, 1], dtype=numpy.int32)
+ans3 =  numpy.asarray([2, 8, 1], dtype=numpy.int32)
+ans1 =  numpy.asarray([1, 3, 4], dtype=numpy.int32)
+ans2 =  numpy.asarray([1, 1, 4], dtype=numpy.int32)
+# s =  numpy.asarray([2, 8, 1, 7, 7, 7, 7, 7, 7, 7], dtype=numpy.float32)
+# test = tensor.eq(x, s)
+# a = test.eval()
+# print a
+#xSub = theano.shared(x)
+probsPadded = tensor.zeros_like(vocab, dtype=numpy.float32)
+probsSubset = probsPadded[context]
+b = tensor.set_subtensor(probsSubset, probs)
+
+ans1probs = b[ans1]
+ans1score = ans1probs.sum()
+ans2probs = b[ans2]
+ans2score = ans2probs.sum()
+ans3probs = b[ans3]
+ans3score = ans3probs.sum()
+allans = tensor.stacklists([ans1score, ans2score, ans3score])
+pred = tensor.argmax(allans)
+
+
+cg = ComputationGraph([ans1probs, ans1score, ans2probs, ans2score, ans3probs, ans3score, allans, pred])
+f = cg.get_theano_function()
+out = f()
+# a = probsPadded.eval()
+# be = b.eval()
+# a1p = ans1probs.eval()
+# a1 = ans1score.eval()
+# print a
+# print be
+# print a1p
+# print a1
+print out

### 2016-04-04 DeepMind-Teaching-Machines-to-Read-and-Comprehend/train.py

@@ -1,0 +1,112 @@
+#!/usr/bin/env python
+
+import logging
+import numpy
+import sys
+import os
+import importlib
+
+import theano
+from theano import tensor
+
+from blocks.extensions import Printing, SimpleExtension, FinishAfter, ProgressBar
+from blocks.extensions.monitoring import DataStreamMonitoring, TrainingDataMonitoring
+from blocks.graph import ComputationGraph
+from blocks.main_loop import MainLoop
+from blocks.model import Model
+from blocks.algorithms import GradientDescent
+
+try:
+    from blocks.extras.extensions.plot import Plot
+    plot_avail = True
+except ImportError:
+    plot_avail = False
+    print "No plotting extension available."
+
+import data
+from paramsaveload import SaveLoadParams
+
+logging.basicConfig(level='INFO')
+logger = logging.getLogger(__name__)
+
+sys.setrecursionlimit(500000)
+
+if __name__ == "__main__":
+    if len(sys.argv) != 2:
+        print >> sys.stderr, 'Usage: %s config' % sys.argv[0]
+        sys.exit(1)
+    model_name = sys.argv[1]
+    config = importlib.import_module('.%s' % model_name, 'config')
+
+    # Build datastream
+    path = os.path.join(os.getenv("DATAPATH"), "deepmind-qa/cnn/questions/training")
+    valid_path = os.path.join(os.getenv("DATAPATH"), "deepmind-qa/cnn/questions/validation")
+    vocab_path = os.path.join(os.getenv("DATAPATH"), "deepmind-qa/cnn/stats/training/vocab.txt")
+
+    ds, train_stream = data.setup_datastream(path, vocab_path, config)
+    _, valid_stream = data.setup_datastream(valid_path, vocab_path, config)
+
+    dump_path = os.path.join("model_params", model_name+".pkl")
+    
+    # Build model
+    m = config.Model(config, ds.vocab_size)
+
+    # Build the Blocks stuff for training
+    model = Model(m.sgd_cost)
+
+    algorithm = GradientDescent(cost=m.sgd_cost,
+                                step_rule=config.step_rule,
+                                parameters=model.parameters)
+    print [v for l in m.monitor_vars for v in l]
+    extensions = [
+            TrainingDataMonitoring(
+                [v for l in m.monitor_vars for v in l],
+                prefix='train',
+                every_n_batches=config.print_freq)
+    ]
+    if config.save_freq is not None and dump_path is not None:
+        extensions += [
[…]

### 2016-04-04 dataset/preprocess_data.py
Small fixes to preprocessing -- replacing newline with ' ' instead of '', special case for 2 newlines in a row, special contraction case for won't.

@@ -158,9 +158,11 @@ def get_entities(story):
 
 def preprocess_story(story):
 	#just '\\newline' will match ''
-	story = re.sub(r'\\newline', '', story)
+	story = re.sub(r'\\newline\\newline', ' ', story)
+	story = re.sub(r'\\newline', ' ', story)
 	story = re.sub(r'\\tab', '', story)
 	#expand contractions, like don't to do not
+	story = re.sub(r'won\'t', 'will not', story)
 	story = re.sub(r'n\'t', ' not', story)
 	#print story
 

### 2016-04-04 DeepMind-Teaching-Machines-to-Read-and-Comprehend/data.py
Changed to support our answer eval format, based on theanotest, and question format from the datastream. Also added mctest-qa (first file only) and changed paths accordingly.  Still in progress.

@@ -19,7 +19,7 @@ logger = logging.getLogger(__name__)
 
 class QADataset(Dataset):
     def __init__(self, path, vocab_file, n_entities, need_sep_token, **kwargs):
-        self.provides_sources = ('context', 'question', 'answer', 'candidates')
+        self.provides_sources = ('context', 'question', 'answer', 'candidates', 'a1', 'a2', 'a3', 'a4')
 
         self.path = path
 
@@ -56,10 +56,18 @@ class QADataset(Dataset):
 
         lines = [l.rstrip('\n') for l in open(os.path.join(self.path, request))]
         #print lines
-        ctx = lines[2]
-        q = lines[4]
-        a = lines[6]
-        cand = [s.split(':')[0] for s in lines[8:]]
+        # ctx = lines[2]
+        # q = lines[4]
+        # a = lines[6]
+        # cand = [s.split(':')[0] for s in lines[8:]]
+        ctx = lines[4]
+        q = lines[6]
+        a = lines[7]
+        a1 = lines[8]
+        a2 = lines[9]
+        a3 = lines[10]
+        a4 = lines[11]
+        cand = [s.split(':')[0] for s in lines[13:]]
 
         entities = range(self.n_entities)
         while len(cand) > len(entities):
@@ -72,7 +80,11 @@ class QADataset(Dataset):
         ctx = self.to_word_ids(ctx, cand_mapping)
         q = self.to_word_ids(q, cand_mapping)
         cand = numpy.array([self.to_word_id(x, cand_mapping) for x in cand], dtype=numpy.int32)
-        a = numpy.int32(self.to_word_id(a, cand_mapping))
+        a = numpy.int32(a) #self.to_word_id(a, cand_mapping))
+        a1 = self.to_word_ids(a1, cand_mapping)
+        a2 = self.to_word_ids(a2, cand_mapping)
+        a3 = self.to_word_ids(a3, cand_mapping)
+        a4 = self.to_word_ids(a4, cand_mapping)
 
         if not a < self.n_entities:
             raise ValueError("Invalid answer token %d"%a)
@@ -87,7 +99,7 @@ class QADataset(Dataset):
         if not numpy.all(q >= 0):
             raise ValueError("Question word id negative: %d"%int(q.min()))
 
-        return (ctx, q, a, cand)
+        return (ctx, q, a, cand, a1, a2, a3, a4)
 
 class QAIterator(IterationScheme):
     requests_examples = True
[…]

### 2016-04-04 DeepMind-Teaching-Machines-to-Read-and-Comprehend/model/attentive_reader.py

@@ -49,9 +49,18 @@ class Model():
         context = tensor.imatrix('context')
         context_mask = tensor.imatrix('context_mask')
         answer = tensor.ivector('answer')
-        # answer = tensor.ivector('answer')
         candidates = tensor.imatrix('candidates')
         candidates_mask = tensor.imatrix('candidates_mask')
+
+        # and the multple choice answers:
+        ans1 = tensor.ivector('ans1')
+        ans1_mask = tensor.ivector('ans1_mask')
+        ans2 = tensor.ivector('ans2')
+        ans2_mask = tensor.ivector('ans2_mask')
+        ans3 = tensor.ivector('ans3')
+        ans3_mask = tensor.ivector('ans3_mask')
+        ans4 = tensor.ivector('ans4')
+        ans4_mask = tensor.ivector('ans4_mask')
 
         bricks = []
 
@@ -60,8 +69,6 @@ class Model():
         question_mask = question_mask.dimshuffle(1, 0)
         context = context.dimshuffle(1, 0)
         context_mask = context_mask.dimshuffle(1, 0)
-        print "question:"
-        print question
 
         # Embed questions and cntext
         embed = LookupTable(vocab_size, config.embed_size, name='question_embed')
@@ -69,6 +76,10 @@ class Model():
 
         qembed = embed.apply(question)
         cembed = embed.apply(context)
+        a1embed = embed.apply(ans1)
+        a2embed = embed.apply(ans2)
+        a3embed = embed.apply(ans3)
+        a4embed = embed.apply(ans4)
 
         qlstms, qhidden_list = make_bidir_lstm_stack(qembed, config.embed_size, question_mask.astype(theano.config.floatX),
                                                      config.question_lstm_size, config.question_skip_connections, 'q')
@@ -121,14 +132,47 @@ class Model():
         probs = out_mlp.apply(tensor.concatenate([attended, qenc], axis=1))
         probs.name = 'probs'
 
-        is_candidate = tensor.eq(tensor.arange(config.n_entities, dtype='int32')[None, None, :],
-                                 tensor.switch(candidates_mask, candidates, -tensor.ones_like(candidates))[:, :, None]).sum(axis=1)
-        probs = tensor.switch(is_candidate, probs, -1000 * tensor.ones_like(probs))
+        # not needed anymore, since we're not only looking at entities
[…]

### 2016-04-04 DeepMind-Teaching-Machines-to-Read-and-Comprehend/train.py

@@ -39,15 +39,15 @@ if __name__ == "__main__":
     config = importlib.import_module('.%s' % model_name, 'config')
 
     # Build datastream
-    path = os.path.join(os.getenv("DATAPATH"), "deepmind-qa/cnn/questions/training")
-    valid_path = os.path.join(os.getenv("DATAPATH"), "deepmind-qa/cnn/questions/validation")
-    vocab_path = os.path.join(os.getenv("DATAPATH"), "deepmind-qa/cnn/stats/training/vocab.txt")
+    path = os.path.join(os.getenv("DATAPATH"), "mctest-qa/questions/training")
+    valid_path = os.path.join(os.getenv("DATAPATH"), "mctest-qa/questions/validation")
+    vocab_path = os.path.join(os.getenv("DATAPATH"), "mctest-qa/stats/training/vocab.txt")
 
     ds, train_stream = data.setup_datastream(path, vocab_path, config)
     _, valid_stream = data.setup_datastream(valid_path, vocab_path, config)
 
     dump_path = os.path.join("model_params", model_name+".pkl")
-    
+
     # Build model
     m = config.Model(config, ds.vocab_size)
 

### 2016-04-04 dataset/preprocess_data.py
modify dataset

@@ -329,11 +329,12 @@ def get_s_q_a_e():
 		question3 = q3 + '\n\n' + answer3 + '\n\n' 
 		question4 = q4 + '\n\n' + answer4 + '\n\n' 
 
-		#four questions in one file
+		'''#four questions in one file
 		qfile = './%s/%s/questions/%d.tsv' % (source, dataset, i)
 		question = info_story + question1 + question2 + question3 + question4 + entity_list
 		with open(qfile, "w") as f:
 			f.write(question)
+
 		
 		#each questions in one file
 		q = []			
@@ -341,6 +342,47 @@ def get_s_q_a_e():
 		question2 = info_story + question2 + entity_list
 		question3 = info_story + question3 + entity_list
 		question4 = info_story + question4 + entity_list
+		q.append(question1) 
+		q.append(question2)
+		q.append(question3) 
+		q.append(question4) 
+
+		for j in range(0, 4):
+			qfile = './%s/%s/questions/%d_q%s.tsv' % (source, dataset, i, j+1)
+			with open(qfile, "w") as f:
+				f.write(q[j])
+		'''
+
+		#each questions with optinal answersin one file
+		q = []			
+		question1 = info_story + q1 + '\n'+ \
+					answer1 + '\n\n' + \
+					preprocess_answer(content[4], entities) + '\n' + \
+					preprocess_answer(content[5], entities) + '\n' + \
+					preprocess_answer(content[6], entities) + '\n' + \
+					preprocess_answer(content[7], entities) + '\n\n' + \
+					entity_list
+		question2 = info_story + q2 + '\n'+ \
+					answer2 + '\n\n' + \
+					preprocess_answer(content[9], entities) + '\n' + \
+					preprocess_answer(content[10], entities) + '\n' + \
+					preprocess_answer(content[11], entities) + '\n' + \
+					preprocess_answer(content[12], entities) + '\n\n' + \
+					entity_list
+		question3 = info_story + q3 + '\n'+ \
+					answer3 + '\n\n' + \
+					preprocess_answer(content[14], entities) + '\n' + \
+					preprocess_answer(content[15], entities) + '\n' + \
+					preprocess_answer(content[16], entities) + '\n' + \
+					preprocess_answer(content[17], entities) + '\n\n' + \
+					entity_list
+		question4 = info_story + q4 + '\n'+ \
+					answer4 + '\n\n' + \
+					preprocess_answer(content[19], entities) + '\n' + \
[…]
